The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-02-14 paper/main.tex
improve text (minor)

The astronomers analyze their data assuming that all stars are
single.  In particular they do not have accurate enough parallaxes to
tell that some of the stars are apparently overluminous.  They want to
compute the number of planets with size $r$ per star of mass $M$.  If
the total number of stars for which such planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are
both large, then the astronomers' estimate for the occurrence rate
($\Lambda$) is simply
\begin{equation}
  \Lambda = \frac{N_{\rm det}}{N_\star}
                    \times \frac{1}{p_{\rm tra}},
\label{eq:occ_rate_simple}
\end{equation}
where the geometric transit probability, $p_{\rm tra}$, accounts for
the fact that most planetary orbits are not aligned close enough with
our line of sight to produce transits.

@@

The other problem is an observational effect. In the searched sample,
the ratio between the number of binary and single stars will differ
from that in a volume-limited sample due to a type of Malmquist bias.
The total luminosity of a binary is larger than the luminosity of
either the primary or secondary star.  This means that for transit
signals of a given amplitude, the binaries are searchable at greater
distances from the Earth.  Thus for any planet and star pair, adding a
stellar companion both helps and hinders transit detection: the extra
photons help by lowering the noise, and hinder by diminishing the
observed transit depth.
% Accounting for each effect requires some care.

@@

We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
at each apparent planet radius and apparent stellar mass\footnote{By
assumption, the apparent stellar mass for single star systems is the
true mass. For binary systems, the apparent mass is the mass of the
primary.}.
Similar to Equation~\ref{eq:rate_density_defn}, we define
$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
per unit stellar mass.  Due to the varying binary mass ratios, we need
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different. The ratio between the number of
binary and single systems for which a transit of depth $\delta$ is
detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
of binary systems in the searchable volume with mass ratio $(q,
q+\mathrm{d}q)$ is now
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\times {n_{\rm b}\over n_{\rm s}}
    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Binaries with larger mass ratios are overrepresented by a factor of
$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
sample of searchable binaries is magnitude-limited.  To obtain
the number of binary systems searched at each $(r\a,M\a)$ pair,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

\subsubsection{Twin binaries}
As a first step, we return to the case where all binaries are twins.
However, we now let the planet radius distribution be a power law,
\begin{equation}
    \Gamma_i(r) = Z_i f(r) = Z_i r^\gamma/\mathcal{N}_r,
\end{equation}
for $\mathcal{N}_r$ the shape function's normalization.  Applying
Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate
density,
\begin{equation}
    \Gamma\a(r\a) = \frac{r\a^{\gamma}}{\mathcal{N}_r} \left[
    \frac{Z_0}{1+\mu}
    +
    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
    \right)
    \right].
    \label{eq:model5_apparent_rate_density}
\end{equation}
Under these assumptions, twin binaries simply shift the apparent
radius distribution: $\Gamma\a(r\a) \propto r\a^\gamma$.  As in
Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.  If planet
occurrence is independent of system multiplicity, the ``correction
factor'' relative to the rate density for singles is
\begin{align}
    \frac{\left. \Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
    &=
    \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
    \label{eq:power_law_correction}
\end{align}
For a binary fraction of $0.1$, $\mu\approx 0.15$. Taking
$\gamma=-2.92$ from \citet{howard_planet_2012},  we find that the
apparent rate density is a mere 0.4\% larger than the rate density of
single stars.
%relative difference $\Delta \Gamma_0 = |\Gamma_0~-~\Gamma\a|/\Gamma_0$
Fortuitously, the exponent of the radius distribution is close to
$-3$, and the errors from neglecting binaries almost entirely
cancel out.

@@

The rate density now varies not only with planet radius, but also
host star mass.  We can absorb this dependence into a power law,
\begin{equation}
    \Gamma_i(r,M) = Z_i \times \frac{r^\gamma}{\mathcal{N}_r} \times
    \frac{M^\zeta}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry
the units.% (each side has units $[r^{-1} M^{-1}]$).

Our main interest is in the apparent rate density's radius
dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
apparent stellar mass, we find that when all stars host the same number
of planets ($Z_0=Z_1=Z_2$),
\begin{align}
    %see annoying_q_factor_dec22.pdf for derivation
    \notag
    \frac{\left.\Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
    &=
    \frac{1}{1+\mu}
    \left[
      1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
    \left(
      \int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\gamma+4}{2}} +
      \right.
      \right. \\
      %isn't latex great?
      &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
      \left.\left.
      \int_0^1 {\rm d}q\,q^{\beta+\gamma+\frac{5}{3}} 
      (1+q^\alpha)^{\frac{3}{2}}
      (1+q^{-\alpha})^{\frac{\gamma+1}{2}}
    \right)
    \right],
    \label{eq:powerlaw_vary_binary}
\end{align}
where $\zeta$ does not appear because of the marginalization over
$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=-2.92$, the
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
$(\ldots)\approx 1.503$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$.
The apparent rate density is 4.8\% larger than the rate density around
singles.  Considering only twin binaries gave us good intuition: for
apparent radii from $2r_\oplus$ to $17r_\oplus$, binarity influences
apparent planet occurrence rates around Sun-like stars at the level of
a few percent.

@@

A common situation during transit survey follow-up is for
high-resolution imaging to reveal multiple stars in a system that
shows planetary transits.  It is often impossible to rule which star
hosts the detected planet.  Intuitively, one would expect that the
primary star would be the more likely host because at fixed
planet size, planetary transits around secondaries have smaller
amplitudes (Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
$\mathcal{D}_2>\mathcal{D}_1$, if $\alpha=3.5$).  However, this
reasoning is qualitative, and its assumptions might not always
hold.

@@

The situation for apparent radii below $2r_\oplus$ is more nuanced.
For the two cases in which secondaries host fewer planets than
primaries, detected planets in binaries are still always more likely
to orbit the primary.  However, if planets exist at the same rate in
primaries and secondaries, then there is a turn-over radius,
$\approx\!0.4r_\oplus$, below which more of the detected planets in
binaries come from secondaries~--~they have all been ``diluted down''
from larger true planetary radii!  Rephrased, going from apparent
radii of $2r_\oplus$ to $1.4r_\oplus$, the fraction of detected
planets with binary companions increases by anywhere from $6\%$ to
$12\%$, depending on the relative occurrence of planets about
primaries and secondaries.  We compare this prediction with recent
observations in Section~\ref{sec:discussion}.
%~\footnote{
%The increase can be derived analytically.  Let the fraction of total
%detected planets from primaries at a given apparent radius be
%$F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm det}^{\rm
%tot}$.  Let the analogous quantity for secondaries be $F_2(r\a)$.  In
%the planet-less secondaries case ($F_2(r\a)=0$), one can analyze
%Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show
%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
%This effect will appear in any radius distribution that declines at
%large radii, and flattens below some cutoff radius, $r_{\rm c}$.  This
%is because (for dilution about primaries) at apparent radii $r\a <
%r_{\rm c}/\sqrt{2}$, relatively more planets will be ``diluted'' into
%the given $r\a$, since there are more planets in the undiluted
%distribution from $r\a$ to $\sqrt{2}r\a$.

@@

In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear
as an island in period-radius space, rather than as a continuous
component of a power law distribution.  This means that the apparent
HJ rates computed in Section~\ref{sec:model_3} are probably
inaccurate.  Instead, let us consider a Gaussian radius shape
function,
\begin{equation}
    f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.  As always,
$\Gamma_i(r) = Z_i f(r)$.  We then compute $\Gamma\a(r\a)$, and plot
it in Figure~\ref{fig:gaussian_HJ}.  Integrating over $r\a >
8r_\oplus$ to find hot Jupiter rates, we find the opposite effect as
in the power law model.  If secondaries host any planets at all, the
apparent HJ rate is {\it greater} than the true rate for singles.  For
instance, if the hot Jupiter rate about secondaries and singles
is equal, then $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
%int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
%For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm
%HJ},0} \approx \Lambda_{\rm HJ,a}$ to within one percent.
Qualitatively, the apparent HJ rate is greater than the true rate for
singles because binary systems have extra uncounted stars that
yield hot Jupiter detections.

@@

This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
straight-forward, but also more tedious, method than that presented in
Section~\ref{sec:general_formula}.   First, note that analogous to
Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
written
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \times \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit
$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
with systems of many different planetary and stellar properties, so
$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
M\a)$  when the true system actually has properties $(r, M)$.
Mathematically,
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_i n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_i \int \mathrm{d}r \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the type of true host star (0: single, 1:
primary, 2: secondary).  The problem reduces to the evaluation of
\begin{equation}
    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and
secondaries in binaries.

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the
true parameters $(r,M)$ is
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int 
      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
Since we assume that binaries are assigned the mass of the primary,
\begin{equation}
    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
    \propto
    \hat{\delta}(M\a-M).
\end{equation}
In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, and the observed depth is
\begin{equation}
    \delta
    = \left[{r\over R(M\a)}\right]^2\times {L(M\a) \over L_{\rm tot}(M\a, q)}
    \equiv \left[{r\over R(M\a)}\right]^2\times 
    \frac{1}{\mathcal{D}_1^2}
    \label{eq:delta_obs_primaries} 
\end{equation}
where
\begin{equation}
    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
\end{equation}
The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
number of binaries that are searchable for a signal $\delta$
and that have mass ratio $q$:
\begin{equation}
    N_\star^0(\delta, 
    L(M\a))\cdot
    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
    \label{eq:primary_normalization}
\end{equation}
Thus,
\begin{align}
    \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
    &=N_\star^0(\delta, L(M\a))
    \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
    \cdot\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
    \label{eq:N_s_1}
\end{align}

\paragraph{Secondaries in binaries}
In this case, $M=qM_1=qM\a$, so
\begin{equation}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    \propto \hat{\delta}\left(M\a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_\star^2$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, but this time
\begin{equation}
      \delta =
      \left[{r\over R(qM\a)}\right]^2 \times
      {L(qM\a) \over L_{\rm tot}(M\a, q)}
      \equiv
      \left[{r\over R(M\a)}\right]^2\times
      \frac{1}{\mathcal{D}_2^2},
\end{equation}
where
\begin{equation}
  \mathcal{D}_2
  =
  \frac{R(qM\a)}{R(M\a)}
  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
\end{equation}
The normalization remains the same as the previous case~--~we are
counting the searchable stars at a given observed depth $\delta$, and
the total luminosity of the binary is the same.  Thus,
\begin{equation}
    \mathcal{N}_\star^2(r\a, M\a; r, M)
    =\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
\end{equation}
where
\begin{align}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    =N_\star^0(\delta, L(M\a)) \cdot \frac{n\b}{n\s} 
    \cdot \mathcal{D}_1^3
    \cdot \hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_2}\right]
    \hat{\delta} \left(M\a-{M\over q}\right).
    \label{eq:mathcal_N_s_2}
\end{align}

>>>>

The astronomers analyze their data assuming that all stars are
single.  In particular they do not have accurate enough parallaxes to
tell that some of the stars are apparently overluminous.  They want to
compute the number of planets with size $r$ per star of mass $M$.  If
the total number of stars for which such planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are
both large, then the astronomers' estimate for the occurrence rate
($\Lambda$) is simply
\begin{equation}
  \Lambda = \frac{N_{\rm det}}{N_\star}
                    \cdot \frac{1}{p_{\rm tra}},
\label{eq:occ_rate_simple}
\end{equation}
where the geometric transit probability, $p_{\rm tra}$, accounts for
the fact that most planetary orbits are not aligned close enough with
our line of sight to produce transits.

@@

The other problem is an observational effect. In the searched sample,
the ratio between the number of binary and single stars will differ
from that in a volume-limited sample due to a type of Malmquist bias.
The total luminosity of a binary is larger than the luminosity of
either the primary or secondary star.  This means that for transit
signals of a given amplitude, the binaries are searchable at greater
distances from the Earth.  Thus for any planet and star pair, adding a
stellar companion both helps and hinders transit detection: the extra
photons help by lowering the noise, and hinder by diminishing the
observed transit depth.

@@

We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
at each apparent planet radius and apparent stellar mass\footnote{By
assumption, the apparent stellar mass for single star systems is the
true mass. For binary systems, the apparent mass is the mass of the
primary.}.
Similar to Equation~\ref{eq:rate_density_defn}, we define
$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
per unit stellar mass.  Due to the varying binary mass ratios, we need
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different. The ratio between the number of
binary and single systems for which a transit of depth $\delta$ is
detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
of binary systems in the searchable volume with mass ratio $(q,
q+\mathrm{d}q)$ is now
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Binaries with larger mass ratios are overrepresented by a factor of
$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
sample of searchable binaries is magnitude-limited.  To obtain
the number of binary systems searched at each $(r\a,M\a)$ pair,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

\subsubsection{Twin binaries}
As a first step, we return to the case where all binaries are twins.
However, we now let the planet radius distribution be a power law,
\begin{equation}
    \Gamma_i(r) = Z_i f(r) = Z_i r^\gamma/\mathcal{N}_r,
\end{equation}
for $\mathcal{N}_r$ the shape function's normalization.  Applying
Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate
density,
\begin{equation}
    \Gamma\a(r\a) = \frac{r\a^{\gamma}}{\mathcal{N}_r} \left[
    \frac{Z_0}{1+\mu}
    +
    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
    \right)
    \right].
    \label{eq:model5_apparent_rate_density}
\end{equation}
Under these assumptions, twin binaries simply shift the apparent
radius distribution: $\Gamma\a(r\a) \propto r\a^\gamma$.  As in
Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.  If planet
occurrence is independent of system multiplicity, the ``correction
factor'' relative to the rate density for singles is
\begin{align}
    \frac{\left. \Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
    &=
    \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
    \label{eq:power_law_correction}
\end{align}
For a binary fraction of $0.1$, $\mu\approx 0.15$. Taking
$\gamma=-2.92$ from \citet{howard_planet_2012},  we find that the
apparent rate density is a mere 0.4\% larger than the rate density of
single stars.  Fortuitously, the exponent of the radius distribution
is close to $-3$, and the errors from neglecting binaries almost
entirely cancel out.

@@

The rate density now varies not only with planet radius, but also
host star mass.  We can absorb this dependence into a power law,
\begin{equation}
    \Gamma_i(r,M) = Z_i \cdot \frac{r^\gamma}{\mathcal{N}_r} \cdot
    \frac{M^\zeta}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry
the units.% (each side has units $[r^{-1} M^{-1}]$).

Our main interest is in the apparent rate density's radius
dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
apparent stellar mass, we find that when all stars host the same number
of planets,
\begin{align}
    %see annoying_q_factor_dec22.pdf for derivation
    \notag
    \frac{\left.\Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
    &=
    \frac{1}{1+\mu}
    \left[
      1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}
    \left(
      \int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\gamma+4}{2}} +
      \right.
      \right. \\
      %isn't latex great?
      &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
      \left.\left.
      \int_0^1 {\rm d}q\,q^{\beta+\gamma+\frac{5}{3}} 
      (1+q^\alpha)^{\frac{3}{2}}
      (1+q^{-\alpha})^{\frac{\gamma+1}{2}}
    \right)
    \right],
    \label{eq:powerlaw_vary_binary}
\end{align}
where $\zeta$ does not appear because of the marginalization over
$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=-2.92$, the
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
$(\ldots)\approx 1.503$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$.
The apparent rate density is 4.8\% larger than the rate density around
singles.  Considering only twin binaries gave us good intuition: for
apparent radii from $2r_\oplus$ to $17r_\oplus$, binarity influences
apparent planet occurrence rates around Sun-like stars at the level of
a few percent.

@@

A common situation during transit survey follow-up is for
high-resolution imaging to reveal multiple stars in a system that
shows planetary transits.  It is often impossible to rule which star
hosts the detected planet.  One would intuitively expect that the
primary star would be the more likely host because at fixed planet
size, planetary transits around secondaries have smaller amplitudes
(Equations~\ref{eq:dil_1} and~\ref{eq:dil_2} imply
$\mathcal{D}_2>\mathcal{D}_1$, if $\alpha=3.5$).  However, this
reasoning is qualitative, and its assumptions might not always hold.

@@

The situation for apparent radii below $2r_\oplus$ is more nuanced.
For the two cases in which secondaries host fewer planets than
primaries, detected planets in binaries are still always more likely
to orbit the primary.  However, if planets exist at the same rate in
primaries and secondaries, then there is a turn-over radius,
$\approx\!0.4r_\oplus$, below which more of the detected planets in
binaries come from secondaries~--~they have all been ``diluted down''
from larger true planetary radii!  Rephrased, going from apparent
radii of $2r_\oplus$~to~$1.4r_\oplus$, the fraction of detected
planets with binary companions increases by anywhere from
$6\%$~to~$12\%$, depending on the relative occurrence of planets about
primaries and secondaries.  We compare this prediction with recent
observations in Section~\ref{sec:discussion}.
%~\footnote{
%The increase can be derived analytically.  Let the fraction of total
%detected planets from primaries at a given apparent radius be
%$F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm det}^{\rm
%tot}$.  Let the analogous quantity for secondaries be $F_2(r\a)$.  In
%the planet-less secondaries case ($F_2(r\a)=0$), one can analyze
%Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show
%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0 }.

@@

In the recent study by~\citet{petigura_CKS_2017}, hot Jupiters appear
as an island in period-radius space, rather than as a continuous
component of a power law distribution.  This means that the apparent
HJ rates computed in Section~\ref{sec:model_3} are probably
inaccurate.  Instead, let us consider a Gaussian radius shape
function,
\begin{equation}
    f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.  As always,
$\Gamma_i(r) = Z_i f(r)$.  We then compute $\Gamma\a(r\a)$, and plot
it in Figure~\ref{fig:gaussian_HJ}.  Integrating over $r\a >
8r_\oplus$ to find hot Jupiter rates, we find the opposite effect as
in the power law model.  If secondaries host any planets at all, the
apparent HJ rate is {\it greater} than the true rate for singles.  For
instance, if the hot Jupiter rate about secondaries and singles
is equal, then $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.81$.
%int_rate_density_vs_radius_model_7_withtext*manyZs.pdf
Qualitatively, the apparent HJ rate is greater than the true rate for
singles because binary systems have extra uncounted stars that
yield hot Jupiter detections.

@@

This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
straight-forward, but also more tedious, procedure than that of
Section~\ref{sec:general_formula}.   First, note that analogous to
Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
written
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \cdot \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit
$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
with systems of many different planetary and stellar properties, so
$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
M\a)$  when the true system actually has properties $(r, M)$.
Mathematically,
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_i n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_i \int \mathrm{d}r \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the type of true host star (0: single, 1:
primary, 2: secondary).  The problem reduces to the evaluation of
\begin{equation}
    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and
secondaries in binaries.

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the
true parameters $(r,M)$ is
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int 
      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
Since we assume that binaries are assigned the mass of the primary,
\begin{equation}
    \mathcal{N}_{{\rm s},q}^1(r\a, M\a, q; r, M)
    \propto
    \hat{\delta}(M\a-M).
\end{equation}
In this case, $\mathcal{N}_{{\rm s},q}^1$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, and the observed depth is
\begin{equation}
    \delta
    = \left[{r\over R(M\a)}\right]^2\cdot {L(M\a) \over L_{\rm tot}(M\a, q)}
    \equiv \left[{r\over R(M\a)}\right]^2\cdot 
    \frac{1}{\mathcal{D}_1^2}
    \label{eq:delta_obs_primaries} 
\end{equation}
where
\begin{equation}
    \mathcal{D}_1=\sqrt{L_{\rm tot}(M\a, q) \over L(M\a)}.
\end{equation}
The normalization of $\mathcal{N}_{{\rm s},q}^1$ is given by the
number of binaries that are searchable for a signal $\delta$
and that have mass ratio $q$:
\begin{equation}
    N_\star^0(r\a, M\a)\cdot
    {n\b\over n\s}\left[L_{\rm tot}(M\a, q) \over L(M\a)\right]^{3/2}.
    \label{eq:primary_normalization}
\end{equation}
where the argument for the number of searchable single stars,
$N_\star^0$, could also be expressed as $(\delta, L(M\a))$.
Applying Equation~\ref{eq:primary_normalization},
\begin{align}
    \mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M)
    &=N_\star^0(r\a, M\a)
    \cdot {n\b\over n\s} \cdot \mathcal{D}_1^3
    \cdot\hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_1}\right]\hat{\delta}(M\a-M).
    \label{eq:N_s_1}
\end{align}

\paragraph{Secondaries in binaries}
In this case, $M=qM_1=qM\a$, so
\begin{equation}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    \propto \hat{\delta}\left(M\a-{M\over q}\right).
    \label{eq:fancyN_s_2_prop}
\end{equation}
Again $\mathcal{N}_\star^2$ is non-zero only at
$r\a=R\a\sqrt{\delta}$, but this time
\begin{equation}
      \delta =
      \left[{r\over R(qM\a)}\right]^2 \cdot
      {L(qM\a) \over L_{\rm tot}(M\a, q)}
      \equiv
      \left[{r\over R(M\a)}\right]^2\cdot
      \frac{1}{\mathcal{D}_2^2},
\end{equation}
where
\begin{equation}
  \mathcal{D}_2
  =
  \frac{R(qM\a)}{R(M\a)}
  \sqrt{ \frac{L_{\rm tot}(M\a,q)}{L(qM\a)} }.
\end{equation}
The normalization remains the same as the previous case~--~we are
counting the searchable stars at a given observed depth $\delta$, and
the total luminosity of the binary is the same.  Thus,
\begin{equation}
    \mathcal{N}_\star^2(r\a, M\a; r, M)
    =\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^2(r\a, M\a, q; r, M),
\end{equation}
where
\begin{align}
    \mathcal{N}_{{\rm s},q}^2(r\a, M\a, q; r, M)
    =N_\star^0(r\a, M\a) \cdot \frac{n\b}{n\s} 
    \cdot \mathcal{D}_1^3
    \cdot \hat{\delta} \left[r\a-\frac{r}{\mathcal{D}_2}\right]
    \hat{\delta} \left(M\a-{M\over q}\right).
    \label{eq:mathcal_N_s_2}
\end{align}
